---
title: "Playing with FOURIER"
output: html_notebook
---
```{r}
rm(list=ls())
options(stringsAsFactors = FALSE)
```

```{r}
library(RCTdesign)
```

```{r}
#***** calculate the number of events using the standard formula:

(1.96 + qnorm(0.9))^2/log(0.85)^2*4

```

```{r}
#** Using RCT design to get the same thing:


#**************** suppose that they actually want 1630 events in a fixed-samples study:
(dsgn <- seqDesign(prob.model="hazard",test.type="less",alt.hypo=0.85,power=0.9))

```
```{r}
(dsgnIA.fda <- seqDesign(prob.model="hazard",test.type="less",sample.size= c(330,1630),alt.hyp=0.85,power="calculate"))

seqPlotPower(dsgnIA.fda,reference = fixed)

dsgnIAnull.fda <- update(dsgnIA.fda,early.stop = 'null')
dsgnIAalt.fda <- update(dsgnIA.fda,early.stop = 'alt') 
dsgnIAasym.5fda <- update(dsgnIA.fda,P=c(.5,.5)) 
dsgnIAasym.7fda <- update(dsgnIA.fda,P=c(.7,.7)) 


#the P parameter is corresponding to null, alt 
#looking at the power - extra chances to stop early protecting

seqInference(dsgnIAnull.fda)

seqPlotBoundary(dsgnIA.fda)
seqPlotPower(dsgnIAalt.fda,dsgnIAasym.5fda,dsgnIAasym.7fda) #lost power

seqPlotBoundary(dsgnIAnull.fda)
seqPlotBoundary(dsgnIAalt.fda)

```

```{r}
(fixed <- seqDesign(prob.model="hazard",test.type="less",sample.size=1630,alt.hyp=0.85,power="calculate"))
seqInference(fixed)
```

this mimics the specific trial using 1630 as sample size
power is higher than the estimated sample size above: .9067


```{r}
#**************** designs with interim analyses:
(dsgnIA.5 <- update(fixed,nbr.analyses=5))

(dsgnIA.4 <- update(fixed,nbr.analyses=4))
(dsgnIA.3 <- update(fixed,nbr.analyses=3))
(dsgnIA.2 <- update(fixed,nbr.analyses=2))
```
```{r}
seqPlotBoundary(dsgnIA.fda,dsgnIAasym.5fda,dsgnIAasym.7fda)
```

```{r}
seqPlotBoundary(dsgnIA.4,dsgnIA.3,dsgnIA.2)
```

Bottom indicates efficacy works and top meaning doesn't work.

```{r}
seqPlotPower(dsgnIA.5,dsgnIA.4,dsgnIA.3,dsgnIA.2,reference=fixed)
abline(v=.85)
```

```{r}
seqPlotASN(dsgnIA.4,dsgnIA.3,dsgnIA.2,reference=fixed)
```

```{r}
seqPlotStopProb(dsgnIA.4)

```


```{r}
(zz3 <- seqOC(dsgnIA.3,theta=0.85))
#names(zz3)
tmp3 <- t(rbind(zz3$lower.stop.prob,zz3$upper.stop.prob,zz3$stop.prob))
apply(tmp3,2,sum)
sum(sampleSize(dsgnIA.3)*tmp3[,3])
#[1] 1255.7
```

```{r}
(zz5 <- seqOC(dsgnIA.5,theta=0.85))

(zz4 <- seqOC(dsgnIA.4,theta=0.85))
# ASN = 1191
(zz3 <- seqOC(dsgnIA.3,theta=0.85))
# ASN = 1258
(zz2 <- seqOC(dsgnIA.2,theta=0.85))
# ASN = 1362
```


```{r}
(dsgnIA2.4 <- update(dsgnIA.4,test.type="two.sided")) 
(dsgnIAnull.4 <- update(dsgnIA.4,early.stop="null")) #highest power power = 0.9022
(dsgnIAalt.4 <- update(dsgnIA.4,early.stop="alt")) #power = .9006
(dsgnIAasym.4 <- update(dsgnIA.4,P=c(1,0.5))) #power = .8654
```

```{r}
(zz2 <- seqOC(dsgnIA.2, theta = 0.85))
# ASN = 1362
(zz3 <- seqOC(dsgnIA.3, theta = 0.85))
# ASN = 1256
(zz4 <- seqOC(dsgnIA.4, theta = 0.85))
# ASN = 1191
(zz4_twosided <- seqOC(dsgnIA2.4,theta=0.85))
# ASN = 1223
(zz4_null <- seqOC(dsgnIAnull.4,theta=0.85))
# ASN = 1610
(zz4_alt <- seqOC(dsgnIAalt.4,theta=0.85))
# ASN = 1223
(zz4_asym <- seqOC(dsgnIAasym.4,theta=0.85)) # Lowest ASN
# ASN = 1112

#Upper is chances not work
#stopping early for benefit (HR is truly .85) is only .2% chance of stopping early
# .7 balance 10% is important
# ASN easier to stop earlier
```

```{r}
(dsgnIA2.3 <- update(dsgnIA.3,test.type="two.sided")) 
(dsgnIAnull.3 <- update(dsgnIA.3,early.stop="null")) #highest power power = 0.9022
(dsgnIAalt.3 <- update(dsgnIA.3,early.stop="alt")) #power = .9006
(dsgnIAasym.3 <- update(dsgnIA.3,P=c(1,0.5))) #power = .8654
(zz3_twosided <- seqOC(dsgnIA2.3,theta=0.85))
# ASN = 1223
(zz3_null <- seqOC(dsgnIAnull.3,theta=0.85))
# ASN = 1610
(zz3_alt <- seqOC(dsgnIAalt.3,theta=0.85))
# ASN = 1223
(zz3_asym <- seqOC(dsgnIAasym.3,theta=0.85)) # Lowest ASN
# ASN = 1112
```

```{r}
par(mfrow = c(1,2))
seqPlotBoundary(dsgnIAnull.4)
seqPlotBoundary(dsgnIAalt.4)
```

```{r}
seqPlotPower(dsgnIA.4,dsgnIAnull.4,reference=fixed)
```

```{r}
seqPlotASN(dsgnIA.4,dsgnIAnull.4,dsgnIAalt.4)
```

```{r}

#seqPlotBoundary(dsgnIA.4,dsgnIAasym.47)


(dsgnIAasym.4 <- update(dsgnIA.4,P=c(1,0.5))) #power = .8654
(dsgnIAasym.47 <- update(dsgnIA.4,P=c(1,0.75))) #power = .8654
seqOC(dsgnIAasym.47,theta = 0.85)
seqInference(fixed)
seqInference(dsgnIAasym.47)
pdf()
seqPlotInference(dsgnIAasym.47)
plotseqInference(dsgnIAasym.47)
```






Which designs are most powerful? stopping at null with 4 interim analysis

seqDesign(prob.model = "hazard", alt.hypothesis = 0.85, nbr.analyses = 4, 
    sample.size = 1630, test.type = "less", power = "calculate", 
    early.stopping = "null")

Which designs have the smallest expected sample size (ASN)? 

seqDesign(prob.model = "hazard", alt.hypothesis = 0.85, nbr.analyses = 4, 
    sample.size = 1630, test.type = "less", power = "calculate", 
    P = c(1, 0.5))

Which designs would tend to stop early?

4 interim analyses are the ones that tend to stop early

seqDesign(prob.model = "hazard", alt.hypothesis = 0.85, nbr.analyses = 4, 
    sample.size = 1630, test.type = "less", power = "calculate", 
    early.stopping = "null")
    
and 

seqDesign(prob.model = "hazard", alt.hypothesis = 0.85, nbr.analyses = 4, 
    sample.size = 1630, test.type = "less", power = "calculate", 
    early.stopping = "alt")
